Open archaeology, open source?

### 2024-04-15 analysis/_06-network.qmd
Add zoom to graphs
Add links to Table 7

@@

```{r tbl-repo-betweenness}
#| tbl-cap: Repositories ranked by centrality to the repository–repository network. Centrality is measured by node betweenness weighted by number of contributions.
oarch_graph_repo_repo |>
  as_tibble() |>
  arrange(-betweenness) |>
  slice(1:10) |>
  left_join(oarch, c("repo" = "gh_repo")) |>
  mutate(n_commits = map_int(gh_commits, nrow)) |>
  unite(tags, tag1:tag5, sep = "; ", na.rm = TRUE) |>
  transmute(rank = row_number(), repo, category, tags, n_commits) |>
  rename(repository = repo, commits = n_commits) |>
  rename_with(tools::toTitleCase) |>
  tt()
```

>>>>

```{r setup-girafe}
set_girafe_defaults(
  opts_zoom = opts_zoom(min = 1, max = 9) 
)
```

@@

```{r tbl-repo-betweenness}
#| tbl-cap: Repositories ranked by centrality to the repository–repository network. Centrality is measured by node betweenness weighted by number of contributions.
oarch_graph_repo_repo |>
  as_tibble() |>
  arrange(-betweenness) |>
  slice(1:10) |>
  left_join(oarch, c("repo" = "gh_repo")) |>
  mutate(n_commits = map_int(gh_commits, nrow)) |>
  unite(tags, tag1:tag5, sep = "; ", na.rm = TRUE) |>
  mutate(repo = glue("[{repo}](https://github.com/{repo})")) |>
  transmute(rank = row_number(), repo, category, tags, n_commits) |>
  rename(repository = repo, commits = n_commits) |>
  rename_with(tools::toTitleCase) |>
  tt() |>
  format_tt(2, markdown = TRUE)
```
